library(lavaan)
math <- read.table("output/math.csv", header=TRUE, sep=",")
noHighCor_math <- read.table("output/noHighCor_math.csv", header=TRUE, sep=",")
all_data <- read.table("output/all_data.csv", header=TRUE, sep=",")
noHighCor_all_data <- read.table("output/noHighCor_all_data.csv", header=TRUE, sep=",")

v <- list()
v$math_items <- read.table("raw_data/math_VariableNames.txt", header=TRUE, sep=",")
v$all_data_items <- read.table("raw_data/VariableNames.txt", header=TRUE, sep=",")
v$noHighCor_all_data <- read.table("raw_data/noHighCor_VariableNames.txt", header=TRUE, sep=",")

# sample size
nrow(math)
nrow(all_data)
# check for missing data
sapply(math, function(X) sum(is.na(X)))
sapply(noHighCor_math, function(X) sum(is.na(X)))
sapply(all_data, function(X) sum(is.na(X)))
sapply(noHighCor_all_data, function(X) sum(is.na(X)))
# Exploratory factor analysis

# check for number of factors
psych::scree(math)
psych::fa.parallel(math)

psych::scree(noHighCor_math)
psych::fa.parallel(noHighCor_math)

psych::scree(all_data)
psych::fa.parallel(all_data)

psych::scree(noHighCor_all_data)
psych::fa.parallel(noHighCor_all_data)

# examine 5 factor EFA for math
sequence <- seq(20)
for (i in sequence)
{
fac1 <- factanal(math, i, rotation = "promax")
}
fac1 <- factanal(math, 1, rotation = "promax")
print(fac1, cutoff = .30)
fl <- round(unclass(fac1$loadings), 2)
fl

write.csv(fl, "output/math-2factor-efa-factor-loadings.csv")

```{r} 
#not working due to missing data

# examine 5 factor EFA for all_data
sequence <- seq(20)
for (i in sequence)
{
  fac1 <- factanal(all_data, i, rotation = "promax")
}
fac1 <- factanal(all_data, 1, rotation = "promax")
print(fac1, cutoff = .30)
fl <- round(unclass(fac1$loadings), 2)
fl
write.csv(fl, "output/all_data-2factor-efa-factor-loadings.csv")
```
```{r} 
# examine factor EFA for all_data
sequence <- seq(20)
for (i in sequence)
{
  i
  fac1 <- factanal(noHighCor_all_data, i, rotation = "promax")
  print(fac1, cutoff = .30)
  fl <- round(unclass(fac1$loadings), 2)
  fl
}
write.csv(fl, "output/noHighCor_all_data-2factor-efa-factor-loadings.csv")
#  fac1 <- factanal(noHighCor_all_data, 1, rotation = "promax")
```



# Confirmatory factor analysis for math data
```{r}
models <- list()
fits <- list()

# paste(v[["math_items"]][["char_VariableNames"]], collapse = " + ")

# one factor model
models$m1 <- 
    'global  =~ CMAT_Addition_Raw + CMAT_Addition_StS + CMAT_Subtraction_Raw + CMAT_Subtraction_StS + CMAT_Multiplication_Raw + CMAT_Multiplication_StS + CMAT_Division_Raw + CMAT_Division_StS + CMAT_BasicCalc_Comp_Quotient + KeyMath_Numeration_Raw + KeyMath_Numeration_ScS + KeyMath_Measurement_Raw + KeyMath_Measurement_ScS + KeyMath_ProblemSolving_Raw + KeyMath_ProblemSolving_ScS + TOMA0x2D2_Attitudes_Raw + TOMA0x2D2_Attitudes_StS'

# two factor model
models$m2 <- 
    ' factor1 =~ CMAT_Addition_Raw + CMAT_Addition_StS + CMAT_Subtraction_Raw + CMAT_Subtraction_StS + CMAT_Multiplication_Raw + CMAT_Multiplication_StS + CMAT_Division_Raw + CMAT_Division_StS + CMAT_BasicCalc_Comp_Quotient + KeyMath_Numeration_Raw + KeyMath_Numeration_ScS + KeyMath_Measurement_Raw + KeyMath_Measurement_ScS + KeyMath_ProblemSolving_Raw + KeyMath_ProblemSolving_ScS

    factor2 =~ TOMA0x2D2_Attitudes_Raw + TOMA0x2D2_Attitudes_StS'

# three factor model
models$m3 <- 
    ' factor1 =~ CMAT_Addition_Raw + CMAT_Addition_StS + CMAT_Subtraction_Raw + CMAT_Subtraction_StS + CMAT_Multiplication_Raw + CMAT_Multiplication_StS + CMAT_Division_Raw + CMAT_Division_StS + CMAT_BasicCalc_Comp_Quotient 

    factor2 =~ KeyMath_Numeration_Raw + KeyMath_Numeration_ScS + KeyMath_Measurement_Raw + KeyMath_Measurement_ScS + KeyMath_ProblemSolving_Raw + KeyMath_ProblemSolving_ScS

    factor3 =~ TOMA0x2D2_Attitudes_Raw + TOMA0x2D2_Attitudes_StS'

# four factor model
models$m4 <- 
    ' factor1 =~ CMAT_Addition_Raw + CMAT_Addition_StS + CMAT_Subtraction_Raw + CMAT_Subtraction_StS 
      
  factor2 =~ CMAT_Multiplication_Raw + CMAT_Multiplication_StS + CMAT_Division_Raw + CMAT_Division_StS + CMAT_BasicCalc_Comp_Quotient 

    factor3 =~ KeyMath_Numeration_Raw + KeyMath_Numeration_ScS + KeyMath_Measurement_Raw + KeyMath_Measurement_ScS + KeyMath_ProblemSolving_Raw + KeyMath_ProblemSolving_ScS

    factor4 =~ TOMA0x2D2_Attitudes_Raw + TOMA0x2D2_Attitudes_StS'


fits$m1 <- lavaan::cfa(models$m1, data = math)
fits$m2 <- lavaan::cfa(models$m2, data = math)
fits$m3 <- lavaan::cfa(models$m3, data = math)
fits$m4 <- lavaan::cfa(models$m3, data = math)

summary(fits$m1, fit.measures = TRUE) 
standardizedSolution(fits$m1)
v$fitindicies <- c("npar",  "chisq", "df", "pvalue", "cfi", "rmsea", 
                 "rmsea.ci.lower", "rmsea.ci.upper", "srmr")
round(sapply(fits, function(X) fitmeasures(X)[v$fitindicies]), 3)


summary(fits$m2, fit.measures = TRUE) 
standardizedSolution(fits$m2)
v$fitindicies <- c("npar",  "chisq", "df", "pvalue", "cfi", "rmsea", 
                 "rmsea.ci.lower", "rmsea.ci.upper", "srmr")
round(sapply(fits, function(X) fitmeasures(X)[v$fitindicies]), 3)


summary(fits$m3, fit.measures = TRUE) 
standardizedSolution(fits$m3)
v$fitindicies <- c("npar",  "chisq", "df", "pvalue", "cfi", "rmsea", 
                 "rmsea.ci.lower", "rmsea.ci.upper", "srmr")
round(sapply(fits, function(X) fitmeasures(X)[v$fitindicies]), 3)
```
# Confirmatory factor analysis for noHighCor_all_data
```{r}
models <- list()
fits <- list()

# 1 factor model 
models$m1 <- 
    'factor1 =~ AWMA0x2DS_VerbalSTM_StS + AWMA0x2DS_VerbalWM_StS + AWMA0x2DS_VisuoSpatialSTM_StS + AWMA0x2DS_VisuoSpatialWM_StS + CMAT_Addition_Raw + CMAT_Subtraction_Raw + CMAT_Multiplication_Raw + CTOPP_EL_Raw + CTOPP_BW_Raw + struggle_reading + reading_disability_tested + tutoring_reading + struggle_math + math_disability_tested + tutoring_math + individual_education_plan0x2F504_plan + KeyMath_Numeration_Raw + KeyMath_ProblemSolving_Raw + KeyMath_ProblemSolving_ScS + TOWRE_SW_Raw + TOWRE_SW_StS + TOWRE_PD_Raw + WASI_Vocab_Raw + WASI_Vocab_T0x2DScore + WASI_BD_Raw + WASI_Sim_Raw + WASI_MR_Raw + WJ0x2DIII_WordID_Raw + WJ0x2DIII_WordID_StS + WJ0x2DIII_WA_Raw + WJ0x2DIII_WA_StS + WJ0x2DIII_PassComp_Raw + WJ0x2DIII_PassComp_StS + WJ0x2DIII_MathFluency_Raw + WJ0x2DIII_MathFluency_StS + WJ0x2DIII_SpatialRelations_Raw + WJ0x2DIII_SpatialRelations_StS'



# 2 factor model 
models$m2 <- 
    'factor1 =~ AWMA0x2DS_VerbalSTM_StS + AWMA0x2DS_VerbalWM_StS + AWMA0x2DS_VisuoSpatialSTM_StS + AWMA0x2DS_VisuoSpatialWM_StS + CMAT_Addition_Raw + CMAT_Subtraction_Raw + CMAT_Multiplication_Raw + CTOPP_EL_Raw + CTOPP_BW_Raw + struggle_reading + tutoring_reading + struggle_math + math_disability_tested + tutoring_math + individual_education_plan0x2F504_plan + KeyMath_Numeration_Raw + KeyMath_ProblemSolving_Raw + KeyMath_ProblemSolving_ScS + TOWRE_SW_Raw + TOWRE_SW_StS + TOWRE_PD_Raw + WASI_Vocab_Raw + WASI_Vocab_T0x2DScore + WASI_BD_Raw + WASI_Sim_Raw + WASI_MR_Raw + WJ0x2DIII_WordID_Raw + WJ0x2DIII_WordID_StS + WJ0x2DIII_WA_Raw + WJ0x2DIII_WA_StS + WJ0x2DIII_PassComp_Raw + WJ0x2DIII_PassComp_StS + WJ0x2DIII_MathFluency_Raw + WJ0x2DIII_MathFluency_StS + WJ0x2DIII_SpatialRelations_Raw + WJ0x2DIII_SpatialRelations_StS

    factor2 =~ CTOPP_RD_StS + struggle_reading + TOWRE_SW_StS + TOWRE_PD_Raw + WJ0x2DIII_WordID_StS + WJ0x2DIII_WA_StS'



# 3 factor model 
models$m3 <- 
    'factor1 =~ AWMA0x2DS_VerbalSTM_StS + AWMA0x2DS_VerbalWM_StS + AWMA0x2DS_VisuoSpatialWM_StS + CTOPP_EL_Raw + CTOPP_BW_Raw + CTOPP_RD_StS + struggle_reading + reading_disability_tested + tutoring_reading + math_disability_tested + individual_education_plan0x2F504_plan + KeyMath_ProblemSolving_ScS + TOWRE_SW_Raw + TOWRE_SW_StS + TOWRE_PD_Raw + WASI_Vocab_T0x2DScore + WJ0x2DIII_WordID_Raw + WJ0x2DIII_WordID_StS + WJ0x2DIII_WA_Raw + WJ0x2DIII_WA_StS + WJ0x2DIII_PassComp_Raw + WJ0x2DIII_PassComp_StS + WJ0x2DIII_MathFluency_StS

    factor2 =~ AWMA0x2DS_VisuoSpatialSTM_StS + AWMA0x2DS_VisuoSpatialWM_StS + CMAT_Addition_Raw + CMAT_Subtraction_Raw + CMAT_Multiplication_Raw + CTOPP_EL_Raw + struggle_math + regular_classroom + father_behavioral_problems + family_history_behavioral_problems + KeyMath_Numeration_Raw + KeyMath_ProblemSolving_Raw + TOMA0x2D2_Attitudes_Raw + WASI_Vocab_Raw + WASI_BD_Raw + WASI_Sim_Raw + WASI_MR_Raw + WJ0x2DIII_MathFluency_Raw + WJ0x2DIII_SpatialRelations_Raw + WJ0x2DIII_SpatialRelations_StS

    factor3 =~ CTOPP_RD_StS + CTOPP_RL_StS + TOWRE_SW_Raw + WJ0x2DIII_MathFluency_Raw'



# 4 factor model 
models$m4 <- 
    'factor1 =~ AWMA0x2DS_VisuoSpatialSTM_StS + CMAT_Addition_Raw + CMAT_Subtraction_Raw + CMAT_Multiplication_Raw + CTOPP_EL_Raw + struggle_math + regular_classroom + father_behavioral_problems + KeyMath_Numeration_Raw + KeyMath_ProblemSolving_Raw + TOMA0x2D2_Attitudes_Raw + TOWRE_SW_Raw + WASI_Vocab_Raw + WASI_BD_Raw + WASI_Sim_Raw + WASI_MR_Raw + WJ0x2DIII_WordID_Raw + WJ0x2DIII_PassComp_Raw + WJ0x2DIII_MathFluency_Raw + WJ0x2DIII_SpatialRelations_Raw

    factor2 =~ AWMA0x2DS_VerbalSTM_StS + AWMA0x2DS_VerbalWM_StS + AWMA0x2DS_VisuoSpatialWM_StS + CTOPP_EL_Raw + CTOPP_BW_Raw + CTOPP_RD_StS + struggle_reading + reading_disability_tested + tutoring_reading + math_disability_tested + individual_education_plan0x2F504_plan + KeyMath_ProblemSolving_ScS + TOWRE_SW_Raw + TOWRE_SW_StS + TOWRE_PD_Raw + WASI_Vocab_T0x2DScore + WJ0x2DIII_WordID_Raw + WJ0x2DIII_WordID_StS + WJ0x2DIII_WA_Raw + WJ0x2DIII_WA_StS + WJ0x2DIII_PassComp_StS + WJ0x2DIII_MathFluency_StS

    factor3 =~ struggle_math + tutoring_math + father_behavioral_problems + father_emotional_problems + father_drug_alcohol_abuse + family_history_learning_problems + family_history_ADD + family_history_behavioral_problems + KeyMath_ProblemSolving_ScS + TOMA0x2D2_Attitudes_Raw

    factor4 =~ CTOPP_RD_StS + CTOPP_RL_StS + TOWRE_SW_Raw + WJ0x2DIII_MathFluency_Raw'



# 5 factor model 
models$m5 <- 
    'factor1 =~ AWMA0x2DS_VisuoSpatialSTM_StS + CMAT_Addition_Raw + CMAT_Subtraction_Raw + CMAT_Multiplication_Raw + CTOPP_EL_Raw + struggle_math + father_behavioral_problems + KeyMath_Numeration_Raw + KeyMath_ProblemSolving_Raw + TOMA0x2D2_Attitudes_Raw + TOWRE_SW_Raw + WASI_Vocab_Raw + WASI_BD_Raw + WASI_Sim_Raw + WASI_MR_Raw + WJ0x2DIII_WordID_Raw + WJ0x2DIII_PassComp_Raw + WJ0x2DIII_MathFluency_Raw + WJ0x2DIII_SpatialRelations_Raw

    factor2 =~ AWMA0x2DS_VerbalSTM_StS + AWMA0x2DS_VerbalWM_StS + AWMA0x2DS_VisuoSpatialWM_StS + CTOPP_EL_Raw + CTOPP_BW_Raw + struggle_reading + KeyMath_ProblemSolving_ScS + TOWRE_SW_Raw + TOWRE_SW_StS + TOWRE_PD_Raw + WASI_Vocab_T0x2DScore + WJ0x2DIII_WordID_Raw + WJ0x2DIII_WordID_StS + WJ0x2DIII_WA_Raw + WJ0x2DIII_WA_StS + WJ0x2DIII_PassComp_StS

    factor3 =~ AWMA0x2DS_VisuoSpatialWM_StS + mother_behavioral_problems + father_behavioral_problems + father_emotional_problems + father_drug_alcohol_abuse + family_history_learning_problems + family_history_behavioral_problems + family_history_neurological_problems + KeyMath_ProblemSolving_ScS + TOMA0x2D2_Attitudes_Raw

    factor4 =~ struggle_reading + reading_disability_tested + tutoring_reading + math_disability_tested + tutoring_math + individual_education_plan0x2F504_plan

    factor5 =~ CTOPP_RD_StS + CTOPP_RL_StS + TOWRE_SW_Raw + TOWRE_PD_Raw + WJ0x2DIII_MathFluency_Raw'



# 6 factor model 
models$m6 <- 
    'factor1 =~ CMAT_Addition_Raw + CMAT_Subtraction_Raw + CMAT_Multiplication_Raw + CTOPP_EL_Raw + struggle_math + KeyMath_Numeration_Raw + KeyMath_ProblemSolving_Raw + TOWRE_SW_Raw + TOWRE_PD_Raw + WASI_Vocab_Raw + WASI_Vocab_T0x2DScore + WASI_BD_Raw + WASI_Sim_Raw + WASI_MR_Raw + WJ0x2DIII_WordID_Raw + WJ0x2DIII_PassComp_Raw + WJ0x2DIII_MathFluency_Raw + WJ0x2DIII_SpatialRelations_Raw

    factor2 =~ AWMA0x2DS_VerbalSTM_StS + AWMA0x2DS_VisuoSpatialWM_StS + CTOPP_EL_Raw + CTOPP_BW_Raw + speech_delay + struggle_reading + KeyMath_ProblemSolving_ScS + TOWRE_SW_Raw + TOWRE_SW_StS + TOWRE_PD_Raw + WJ0x2DIII_WordID_Raw + WJ0x2DIII_WordID_StS + WJ0x2DIII_WA_Raw + WJ0x2DIII_WA_StS + WJ0x2DIII_PassComp_StS

    factor3 =~ AWMA0x2DS_VisuoSpatialSTM_StS + AWMA0x2DS_VisuoSpatialWM_StS + struggle_math + tutoring_math + mother_behavioral_problems + father_behavioral_problems + father_emotional_problems + father_drug_alcohol_abuse + family_history_behavioral_problems + KeyMath_ProblemSolving_ScS + TOMA0x2D2_Attitudes_Raw + WJ0x2DIII_MathFluency_StS + WJ0x2DIII_SpatialRelations_StS

    factor4 =~ struggle_reading + reading_disability_tested + tutoring_reading + math_disability_tested + tutoring_math + individual_education_plan0x2F504_plan

    factor5 =~ CTOPP_RD_StS + CTOPP_RL_StS

    factor6 =~ WASI_Vocab_Raw + WASI_Vocab_T0x2DScore'



# 7 factor model 
models$m7 <- 
    'factor1 =~ CMAT_Addition_Raw + CMAT_Subtraction_Raw + CMAT_Multiplication_Raw + KeyMath_Numeration_Raw + KeyMath_ProblemSolving_Raw + TOWRE_SW_Raw + TOWRE_PD_Raw + WASI_Vocab_Raw + WASI_BD_Raw + WASI_Sim_Raw + WASI_MR_Raw + WJ0x2DIII_WordID_Raw + WJ0x2DIII_PassComp_Raw + WJ0x2DIII_MathFluency_Raw

    factor2 =~ AWMA0x2DS_VerbalSTM_StS + AWMA0x2DS_VisuoSpatialWM_StS + CTOPP_EL_Raw + CTOPP_BW_Raw + speech_delay + struggle_reading + KeyMath_ProblemSolving_ScS + TOWRE_SW_Raw + TOWRE_SW_StS + TOWRE_PD_Raw + WASI_Vocab_T0x2DScore + WJ0x2DIII_WordID_Raw + WJ0x2DIII_WordID_StS + WJ0x2DIII_WA_Raw + WJ0x2DIII_WA_StS + WJ0x2DIII_PassComp_StS + WJ0x2DIII_MathFluency_StS

    factor3 =~ speech_delay + father_behavioral_problems + father_emotional_problems + father_drug_alcohol_abuse + family_history_learning_problems + family_history_ADD + family_history_behavioral_problems + KeyMath_ProblemSolving_ScS + TOMA0x2D2_Attitudes_Raw + WJ0x2DIII_MathFluency_StS

    factor4 =~ struggle_reading + reading_disability_tested + tutoring_reading + math_disability_tested + tutoring_math + individual_education_plan0x2F504_plan

    factor5 =~ AWMA0x2DS_VisuoSpatialSTM_StS + AWMA0x2DS_VisuoSpatialWM_StS + learning_preference_teacher + learning_preference_discussions + WASI_BD_Raw + WASI_MR_Raw + WJ0x2DIII_SpatialRelations_Raw + WJ0x2DIII_SpatialRelations_StS

    factor6 =~ CTOPP_RD_StS + CTOPP_RL_StS

    factor7 =~ WASI_Vocab_Raw + WASI_Vocab_T0x2DScore'



# 8 factor model 
models$m8 <- 
    'factor1 =~ CMAT_Addition_Raw + CMAT_Subtraction_Raw + CMAT_Multiplication_Raw + KeyMath_Numeration_Raw + KeyMath_ProblemSolving_Raw + TOWRE_SW_Raw + TOWRE_PD_Raw + WASI_Vocab_Raw + WASI_BD_Raw + WASI_Sim_Raw + WASI_MR_Raw + WJ0x2DIII_WordID_Raw + WJ0x2DIII_PassComp_Raw + WJ0x2DIII_MathFluency_Raw

    factor2 =~ AWMA0x2DS_VerbalSTM_StS + AWMA0x2DS_VisuoSpatialWM_StS + CTOPP_EL_Raw + CTOPP_BW_Raw + speech_delay + struggle_reading + KeyMath_ProblemSolving_ScS + TOWRE_SW_Raw + TOWRE_SW_StS + TOWRE_PD_Raw + WASI_Vocab_T0x2DScore + WJ0x2DIII_WordID_Raw + WJ0x2DIII_WordID_StS + WJ0x2DIII_WA_Raw + WJ0x2DIII_WA_StS + WJ0x2DIII_PassComp_StS

    factor3 =~ AWMA0x2DS_VisuoSpatialSTM_StS + AWMA0x2DS_VisuoSpatialWM_StS + tutoring_math + regular_classroom + learning_preference_teacher + learning_preference_discussions + KeyMath_ProblemSolving_ScS + WASI_BD_Raw + WASI_MR_Raw + WJ0x2DIII_SpatialRelations_Raw + WJ0x2DIII_SpatialRelations_StS

    factor4 =~ speech_delay + mother_behavioral_problems + father_speech_problems + father_emotional_problems + father_drug_alcohol_abuse + family_history_learning_problems + family_history_ADD + family_history_behavioral_problems + family_history_neurological_problems

    factor5 =~ struggle_reading + reading_disability_tested + tutoring_reading + math_disability_tested + tutoring_math + individual_education_plan0x2F504_plan

    factor6 =~ CTOPP_RD_StS + CTOPP_RL_StS

    factor7 =~ WJ0x2DIII_MathFluency_Raw + WJ0x2DIII_MathFluency_StS

    factor8 =~ WASI_Vocab_Raw + WASI_Vocab_T0x2DScore'



# 9 factor model 
models$m9 <- 
    'factor1 =~ CMAT_Addition_Raw + CMAT_Subtraction_Raw + CMAT_Multiplication_Raw + CTOPP_EL_Raw + KeyMath_Numeration_Raw + KeyMath_ProblemSolving_Raw + TOWRE_SW_Raw + TOWRE_PD_Raw + WASI_Vocab_Raw + WASI_BD_Raw + WASI_Sim_Raw + WASI_MR_Raw + WJ0x2DIII_WordID_Raw + WJ0x2DIII_PassComp_Raw + WJ0x2DIII_MathFluency_Raw + WJ0x2DIII_SpatialRelations_Raw

    factor2 =~ AWMA0x2DS_VerbalSTM_StS + TOWRE_PD_Raw + WJ0x2DIII_WA_Raw + WJ0x2DIII_WA_StS + WJ0x2DIII_PassComp_Raw

    factor3 =~ struggle_reading + reading_disability_tested + tutoring_reading + math_disability_tested + tutoring_math + individual_education_plan0x2F504_plan

    factor4 =~ speech_delay + TOWRE_SW_Raw + TOWRE_SW_StS + TOWRE_PD_Raw + WJ0x2DIII_WordID_Raw + WJ0x2DIII_WordID_StS + WJ0x2DIII_WA_StS + WJ0x2DIII_PassComp_StS

    factor5 =~ speech_delay + father_speech_problems + father_medical_problems + father_emotional_problems + father_drug_alcohol_abuse + family_history_learning_problems + family_history_ADD + family_history_behavioral_problems + KeyMath_ProblemSolving_ScS

    factor6 =~ CTOPP_RD_StS + CTOPP_RL_StS

    factor7 =~ KeyMath_ProblemSolving_ScS + WASI_Vocab_Raw + WASI_Vocab_T0x2DScore

    factor8 =~ AWMA0x2DS_VisuoSpatialSTM_StS + AWMA0x2DS_VisuoSpatialWM_StS + learning_preference_discussions + WASI_BD_Raw + WASI_MR_Raw + WJ0x2DIII_SpatialRelations_Raw + WJ0x2DIII_SpatialRelations_StS

    factor9 =~ WJ0x2DIII_MathFluency_Raw + WJ0x2DIII_MathFluency_StS'





#lavaan WARNING: some observed variances are (at least) a factor 1000 times larger than others; use varTable(fit) to investiga
fits$m1 <- lavaan::cfa(models$m1, data = noHighCor_all_data)
fits$m2 <- lavaan::cfa(models$m2, data = noHighCor_all_data)
fits$m3 <- lavaan::cfa(models$m3, data = noHighCor_all_data)
fits$m4 <- lavaan::cfa(models$m4, data = noHighCor_all_data)
fits$m5 <- lavaan::cfa(models$m5, data = noHighCor_all_data)

#lavaan WARNING: some observed variances are (at least) a factor 1000 times larger than others; use varTable(fit) to investiga
#telavaan WARNING:
#    Could not compute standard errors! The information matrix could
#    not be inverted. This may be a symptom that the model is not
#    identified.lavaan WARNING: some estimated ov variances are negativelavaan WARNING: not all elements of the #gradient are (near) zero;
#                  the optimizer may not have found a local solution;
#                  use lavInspect(fit, "optim.gradient") to investigate
fits$m6 <- lavaan::cfa(models$m6, data = noHighCor_all_data)
fits$m7 <- lavaan::cfa(models$m7, data = noHighCor_all_data)
fits$m8 <- lavaan::cfa(models$m8, data = noHighCor_all_data)
fits$m9 <- lavaan::cfa(models$m9, data = noHighCor_all_data)


summary(fits$m3, fit.measures = TRUE) 
standardizedSolution(fits$m3)

v$fitindicies <- c("npar",  "chisq", "df", "pvalue", "cfi", "rmsea", 
                 "rmsea.ci.lower", "rmsea.ci.upper", "srmr")

round(sapply(fits, function(X) fitmeasures(X)[v$fitindicies]), 3)
```
